%!TEX program = lualatex

\documentclass[11pt, twoside]{article}

\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{csquotes}
\MakeOuterQuote{"}
\setmainfont[Renderer=Basic, Numbers=OldStyle, Scale = 1.0]{Palatino Linotype}
\setsansfont{Gill Sans MT}
\setmonofont{Andale Mono}
\usepackage{microtype}
\setlength{\parindent}{2em}
\setlength{\parskip}{1em}
\usepackage[hidelinks]{hyperref}
\usepackage{titling}

\pretitle{\begin{center}\begin{Large}\begin{textsf}}
\posttitle{\end{textsf}\end{Large}\end{center}}
\preauthor{}%
\postauthor{}%
\predate{}%
\postdate{}%
\setlength{\droptitle}{-4em}

\title{What Is Privilege?}
\author{}
\date{}

\begin{document}

	\maketitle

	\begin{center}\textit{Source:} \url{http://www.buzzfeed.com/dayshavedewi/what-is-privilege}\end{center}

	\begin{enumerate}
		\item If your parents worked nights and weekends to support your family, take one step back.
		\item If you are able to move through the world without fear of sexual assault, take one step forward.
		\item If you can show affection for your romantic partner in public without fear of ridicule or violence, take one step forward.
		\item If you have ever been diagnosed as having a physical or mental illness/disability, take one step back.
		\item If the primary language spoken in your household growing up was not English, take one step back.
		\item If you came from a supportive family environment take one step forward.
		\item If you have ever tried to change your speech or mannerisms to gain credibility, take one step back.
		\item If you can go anywhere in the country, and easily find the kinds of hair products you need and/or cosmetics that match your skin color, take one step forward.
		\item If you were embarrassed about your clothes or house while growing up, take one step back.
		\item If you can make mistakes and not have people attribute your behavior to flaws in your racial/gender group, take one step forward.
		\item If you can legally marry the person you love, regardless of where you live, take one step forward.
		\item If you were born in the United States, take one step forward.
		\item If you or your parents have ever gone through a divorce, take one step back.
		\item If you felt like you had adequate access to healthy food growing up, take one step forward
		\item If you are reasonably sure you would be hired for a job based on your ability and qualifications, take one step forward.
		\item If you would never think twice about calling the police when trouble occurs, take one step forward.
		\item If you can see a doctor whenever you feel the need, take one step forward.
		\item If you feel comfortable being emotionally expressive/open, take one step forward.
		\item If you have ever been the only person of your race/gender/socio-economic status/sexual orientation in a classroom or workplace setting, please take one step back.
		\item If you took out loans for your education take one step backward.
		\item If you get time off for your religious holidays, take one step forward.
		\item If you had a job during your high school and college years, take one step back.
		\item If you feel comfortable walking home alone at night, take one step forward.
		\item If you have ever traveled outside the United States, take one step forward.
		\item If you have ever felt like there was NOT adequate or accurate representation of your racial group, sexual orientation group, gender group, and/or disability group in the media, take one step back.
		\item If you feel confident that your parents would be able to financially help/support you if you were going through a financial hardship, take one step forward.
		\item If you have ever been bullied or made fun of based on something that you can’t change, take one step back.
		\item If there were more than 50 books in your house growing up, take one step forward.
		\item If you studied the culture or the history of your ancestors in elementary school take one step forward.
		\item If your parents or guardians attended college, take one step forward.
		\item If you ever went on a family vacation, take one step forward.
		\item If you can buy new clothes or go out to dinner when you want to, take one step forward.
		\item If you were ever offered a job because of your association with a friend or family member, take one step forward.
		\item If one of your parents was ever laid off or unemployed not by choice, take one step back.
		\item If you were ever uncomfortable about a joke or a statement you overheard related to your race, ethnicity, gender, appearance, or sexual orientation but felt unsafe to confront the situation, take one step back.
	\end{enumerate}
\end{document}